---
title: "my-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(ryx)
library(MASS)
```

# ryx Package

## Introduction 

The ryx package give you tools to calculate and visualize correlations
within a given data set. The main function is the ryx() function. Additional 
functions to support ryx include print.ryx(), summarize.ryx() and plot.ryx().

## Main Function 

The ryx function prints a table of correlations between a dependent variable y and one or more independent x variables. The format of the function is ryx(data, y, x, digits=3). Data is a data frame, y is the name of a numeric variable in the data frame, x is a character vector with the names of one or more numeric variables in the data frame, digits indicates the number of decimal places to print (3 is the default). If the user does not indicate x, the function will return the correlation of y with every other numeric variable in the data frame. 

### Example 

```{r example}
ryx(mtcars, y = "mpg", x = c("hp", "wt", "disp", "cyl", "am", "gear"))
```

## Print Function 

The print function takes correlations created by the ryx function and prints a table of correlations that notes when the p value is < 2e-16. 

### Example 

```{r}
x <- ryx(Boston, y="medv")
x
```


## Summary Function 

The summary function takes correlations created by the ryx function and prints
a summary of the median correlation, the range,and how many variables are significant
at the p < 0.05 level. 

### Example 

```{r}
x <- ryx(Boston, y="medv")
summary(x)
```


## Plot Function 

The plot function takes correlations created by the ryx function and prints a plot of r values.

### Example 

```{r}
x <- ryx(Boston, y="medv")
plot(x)
```
